%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Hieu Do - Resume
% 7/26/2016
%
% Reference:
% Debarghya Das (http://debarghyadas.com)

\documentclass[]{hieudo-build}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Kevin Mui}
{\urlstyle{same}
	\faGlobe \href{http://pages.cs.wisc.edu/~mui/}{ pages.cs.wisc.edu/~mui}\\
	\faEnvelope \href{mailto:kmui2@wisc.edu}{ kmui2@wisc.edu}\\
	\faGithub \href{https://github.com/kmui2}{   github.com/kmui2}\\
	\faLinkedinSquare \href{https://www.linkedin.com/in/kmui2}{   linkedin.com/in/kmui2}\\
    \faFile \href{https://devpost.com/kmui2}{devpost.com/kmui2}
}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.34\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{UW Madison}
\descript{College of Engineering}
BS in Computer Science  and\\
in Computer Engineering \\
Expected Grad. May 2019 \\
Cum. GPA: 3.827\\
\sectionsep

\subsection{Appleton West HS}
Grad. June 2015 \\
GPA: 3.9 \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
% \subsection{Programming}
\location{Languages:}

HTML/CSS/JavaScript, Java
\\Python, C++, C, SQL

\location{Frameworks:}
Angular 2, NodeJS, Ionic, 
\\Twitter Bootstrap 
\\MeteorJS \& Phaser (Prior exp.) \\

\location{Databases:}
Firebase, MongoDB (Prior exp.) \\

% \sectionsep
% \subsection{Languages}
% \location{Native fluency:} English, Vietnamese\\
\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     HACKATHONS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Hackathons}
% HuskieHacks \textbullet{} HackIllinois \\
% MadHacks \textbullet{} WildHacks\\
% \sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
Object-Oriented Programming\\
Data Structures \\
Discrete Mathematics \\
Artificial Intelligence \\
Computer Graphics \\
Machine Organization (some OS) \\
Database Management
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ADDITIONAL INFORMATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Activities}
Hackathon Competitor \\
Project Lead The Way\\
'14 \& '15 National Science Bowl\\
Fox Valley Math League 
\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     AWARDS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% Dean's List\\
% NYU PROMISE Scholarship\\
% Shelby C. Davis Scholarship\\
% President’s Circle Scholarship\\
% \sectionsep

\sectionsep
\DTMsetdatestyle{mylastupdate}
\DTMdisplaydate{\the\year}{\the\month}{\the\day}{-1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\workplace{UW Informatics Skunkworks}{Sept 2016 – Present}\\
\position{Student Researcher}{Madison, WI}
\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Building a neural network using APIs including Google's TensorFlow and MATLAB as tools for research in Materials Science.
\item Focusing primarily on predicting Perovskite compositions that would be practical for use in computing devices.
\end{tightemize}
\sectionsep

\workplace{Computer Science Learning Center}{Jan 2017 – Present} \\
\position{Computer Science Tutor}{Madison, WI}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Drop-in tutoring students in UW CS courses (Intro to Java, Python, and Data Structures).
\item Meet weekly with other tutors and a CS faculty instructors in innovating the CS department's curriculum.
\end{tightemize}
\sectionsep

\workplace{UW Housing }{Sept 2015 – May 2017} \\
\position{Student Facility Worker}{Madison, WI}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Learning life skills from cooking to managing cleanliness, cooperating with chefs and supervisors, and using time management including both personal and professional.
\end{tightemize}
\sectionsep

% \runsubsection{The Westminster News} \\
% \descript{Co-Editors-in-Chief (2014) | Layout Editor (2012) }
% \location{Sep 2012 – May 2015 | Simsbury, CT}
% \begin{tightemize}
% \item Led 30+ staff at a 400-student boarding school to publish the monthly school newspaper.
% \item Consulted in layout design and technology application.
% \end{tightemize}
% \sectionsep

% \runsubsection{VietAbroader Organization} \\
% \descript{Program Assistant Manager | VAPedia Associate }
% \location{Mar 2013 – Mar 2014 | Ho Chi Minh City, Vietnam}
% \begin{tightemize}
% \item VietAbroader is a non-profit organization run by Vietnamese students abroad.
% \item Designed the high school content for the VAPedia website.
% \item Assisted in recruiting guest speakers and volunteers for VietAbroader Study-Abroad Conference 2013.
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\runsubsection{Neural Network\faGithub}
\descript{}
[Research] A working project coded in TensorFlow to predict stabilities of Perovskite compositions given their measurable properties.
\sectionsep

\runsubsection{Graphics Town\faGithub}
\descript{}
[Class Project] An Object-Oriented WebGL (JavaScript) application that can render 3D graphics and motion on a web browser.
\sectionsep

\runsubsection{Giphy Flashcards\faGithub}
\descript{}
[Personal] A Web and Mobile Flashcard App built using Angular 2 and Ionic respectively that helps students learn new languages using the Giphy API. Has a functional login and database system using Firebase.
\sectionsep 

\runsubsection{Trash-Dove Game\faGithub}
\descript{}
[Personal] A JavaScript game built using Physics and 2D Graphics APIs. Also utilizes the Firebase Database to read and save world data.
\sectionsep

\runsubsection{Struggle in the Aquarium\faGithub}
\descript{}
[Hackathon] A 2D shooter game built using P5JS API.
\sectionsep 

\end{minipage} 

\end{document}  
